Quantitative Evaluation of Touch-Screen Performance with Transition Matrix Measures

### 2015-09-14 flux-entropy-paper/flux-entropy-paper.tex
cleaned up figures a bit

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/flux-entropy-distribution}
  \caption{Distribution of flux and entropy by performance type and
    context. Flux and entropy tended to be linearly related in
    improvisations, particularly in demonstrations and studies, while
    compositions had a more scattered relationship.
    \label{fig:flux-entropy-distribution}}
\end{figure}

The distribution of flux and entropy with respect to session contexts,
types and instrumentation are shown in Figures
\ref{fig:flux-entropy-boxplot} and
\ref{fig:flux-entropy-distribution}. A three-way ANOVA procedure was
performed on the data set to find whether the metatdata could
significantly predict the entropy and flux values.
% TODO we haven't explained what ``the 95 performative sessions'' are,
% have we?
In the following analysis, only the 95 performative sessions were
considered (i.e.~not the demonstration or data collection contexts).

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/type-section-flux}
\includegraphics[width=\linewidth]{figures/type-section-entropy}
  \caption{The flux of compositions and improvisations divided into
    beginning, middle, and end. Composition flux remains stable throughout,
    but improvisations show a downward trend and composition entropy tends to move up
    at the end, while flux moves down.
    \label{fig:type-section-flux-entropy}}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/context-section-flux}
  \includegraphics[width=\linewidth]{figures/context-section-entropy}
  \caption{The distribution of flux and entropy in performances divided by ``beginnings,
    middles, and ends''.
    \label{fig:context-section-flux-entropy}}
\end{figure}

>>>>

\usepackage{subcaption}

@@

% \begin{figure}
%   \centering
%   \includegraphics[width=\linewidth]{figures/flux-entropy-distribution}
%   \caption{Distribution of flux and entropy by performance type and
%     context. Flux and entropy tended to be linearly related in
%     improvisations, particularly in demonstrations and studies, while
%     compositions had a more scattered relationship.
%     \label{fig:flux-entropy-distribution}}
% \end{figure}

The distribution of flux and entropy with respect to session contexts,
types and instrumentation are shown in Figure
\ref{fig:flux-entropy-boxplot}. A three-way ANOVA procedure was
performed on the data set to find whether the metatdata could
significantly predict the entropy and flux values.
% TODO we haven't explained what ``the 95 performative sessions'' are,
% have we?
In the following analysis, only the 95 performative sessions were
considered (i.e.~not the demonstration or data collection contexts).

@@

\begin{figure*}[t!]
    \centering
    \begin{subfigure}[t]{0.4\linewidth}
        \centering
          \includegraphics[width=\linewidth]{figures/type-section-flux}
          \includegraphics[width=\linewidth]{figures/type-section-entropy}
          \caption{Performances divided by performance type. \label{fig:type-section-flux-entropy}}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.4\linewidth}
        \centering
          \includegraphics[width=\linewidth]{figures/context-section-flux}
          \includegraphics[width=\linewidth]{figures/context-section-entropy}
          \caption{Sessions divided by performance context. \label{fig:context-section-flux-entropy}}
    \end{subfigure}
    \caption{The flux and entropy of different interaction sessions
      divided into beginning, middle, and end.}
\end{figure*}

@@

% \begin{figure}
%   \centering
%   \includegraphics[width=\linewidth]{figures/type-section-flux}
%   \includegraphics[width=\linewidth]{figures/type-section-entropy}
%   \caption{The flux of compositions and improvisations divided into
%     beginning, middle, and end. Composition flux remains stable throughout,
%     but improvisations show a downward trend and composition entropy tends to move up
%     at the end, while flux moves down.
%     \label{fig:type-section-flux-entropy}}
% \end{figure}

% \begin{figure}
%   \centering
%   \includegraphics[width=\linewidth]{figures/context-section-flux}
%   \includegraphics[width=\linewidth]{figures/context-section-entropy}
%   \caption{The distribution of flux and entropy in performances divided by ``beginnings,
%     middles, and ends''.
%     \label{fig:context-section-flux-entropy}}
% \end{figure}
